
 % ***********************************************************************************
 % ---------------------            BIBLIOGRAFIA                 ---------------------
 % ***********************************************************************************

\chapter*{Bibliografia}

%\bibliographystyle{unsrt}
%\bibliography{/home/sb/LatexStuffs/books}
%\addcontentsline{toc}{chapter}{Bibliografía}
\begin{thebibliography}{X}
\bibitem{1} \textsc{Zahid Farid, Rosdiadee Nordin} y \textsc{Mahamod Ismail}, <<Recent Advances in Wireless Indoor Localization Techniques
and System>>, \textit{Journal of Computer Networks and Communications}, 2013.
\bibitem{2} \textsc{Zhao Kai, Li Binghao} y \textsc{Andrew Dempster}, <<A Comparison of algorithms adopted in fingerprinting indoor positioning systems>>, \textit{IGNSS Symposium}, 2013.
\bibitem{3} \textsc{Mayur Tawari},\textsc{Onkar Pathak},\textsc{Rajesh Palaskar} y \textsc{Rajesh Palkar}, <<Wi-Fi Indoor Positioning System Based on RSSI Measurements from Wi-Fi Access Points –A Tri-lateration Approach>>, \textit{International Journal of Scientific \& Engineering Research. V5}, 2014.
\bibitem{4} \textsc{Habibi Lashkari, Arash \& Parhizkar, Behrang \& Ng Ah Ngan, Mike.} (2010). <<WIFI-based indoor positioning system>>. Computer and Network Technology, International Conference on. 76-78. 10.1109/ICCNT.2010.33. 
\bibitem{5} \textsc{C. Yang and H. r. Shao}, <<WiFi-based indoor positioning,>> in IEEE Communications Magazine, vol. 53, no. 3, pp. 150-157, March 2015. doi: 10.1109/MCOM.2015.7060497
\bibitem{6} \textsc{Chua Ching, Jeleen, Domingo, Carolyn, Iglesia, Kyla, et al.}, <<Mobile Indoor Positioning Using Wi-fi Localization and Image Processing>>, Theory and Practice of Computation (2013) Springer Japan.
\bibitem{7} \textsc{Bianca Bobescu, Marian Alexandru} <<Mobile indoor positioning using Wifi localization>> Review of the Air Force Academy. Transilvania University, Brasov, Romania
\bibitem{8} \textsc{Ma, R., Guo, Q., Hu, C., \& Xue, J.} (2015). <<An Improved WiFi Indoor Positioning Algorithm by Weighted Fusion>>. Sensors.
\bibitem{9} \textsc{Chou, Yun-Chih.} <<Characterizing Wi-Fi Network Discovery.>> 10.13140/RG.2.2.36542.18241.(2017).
\end{thebibliography}